Run models

### 2017-02-01 Code/run-models.Rmd

```{r fit_models_alabama_males}
#run time: expect 2 hours
#fit the bayesian models and put the 1000 posterior samples into a data frame
system.time(
  for(sex_i in c("Male", "Female")){
    #for(state_i in c("Alabama", "Arizona", "Arkansas", "California")) { #saved as results_set_1
    for(state_i in c("Colorado", "Connecticut", "Delaware", "Washington DC")) { #saved as results_set_2
      assign(paste0("r.White.", gsub(" ", "", state_i), ".", sex_i), run_analysis(dataset = dat.clean, state1 = state_i, sex1 = sex_i, race1 = "White"))
      assign(paste0("r.Black.", gsub(" ", "", state_i), ".", sex_i), run_analysis(dataset = dat.clean, state1 = state_i, sex1 = sex_i, race1 = "Black"))
    }
  }
)

# r.White <- rbind(r.White.AlabamaMale, r.White.ArizonaMale, r.White.ArkansasMale, r.White.CaliforniaMale,
#                  r.White.AlabamaFemale, r.White.ArizonaFemale, r.White.ArkansasFemale, r.White.CaliforniaFemale)
r.White <- rbind(r.White.Colorado.Male, r.White.Connecticut.Male, r.White.Delaware.Male, r.White.WashingtonDC.Male,
                 r.White.Colorado.Female, r.White.Connecticut.Female, r.White.Delaware.Female, r.White.WashingtonDC.Female)
r.White$race <- "White"

# r.Black <- rbind(r.Black.AlabamaMale, r.Black.ArizonaMale, r.Black.ArkansasMale, r.Black.CaliforniaMale,
#                  r.Black.AlabamaFemale, r.Black.ArizonaFemale, r.Black.ArkansasFemale, r.Black.CaliforniaFemale)
r.White <- rbind(r.Black.Colorado.Male, r.Black.Connecticut.Male, r.Black.Delaware.Male, r.Black.WashingtonDC.Male,
                 r.Black.Colorado.Female, r.Black.Connecticut.Female, r.Black.Delaware.Female, r.Black.WashingtonDC.Female)
r.Black$race <- "Black"
```

@@

le.calculations = vector(mode = "list", length = n)
counter = 1
system.time(
  for (stratum_i in levels(droplevels(r.All$state.year.sex))){

@@

#SET 2: Colorado, Connecticut, Delaware, Washington DC
save(r.All, le.calculations, file = "~/BW_results/results_set_2.Rdata") 
write.csv(x = BlackWhite, file = "~/BlackWhiteMortalityGap/Results/BlackWhite_set_2.csv")
write.csv(x = age.decomp.estimates, file = "~/BlackWhiteMortalityGap/Results/age_decomp_set_2.csv")
write.csv(x = cod.marginal.estimates, file = "~/BlackWhiteMortalityGap/Results/cod_marginal_set_2.csv")
write.csv(x = age.cod.estimates, file = "~/BlackWhiteMortalityGap/Results/age_cod_set_2.csv")
```

>>>>

```{r fit_models}
#run time: expect 2 hours
#fit the bayesian models and put the 1000 posterior samples into a data frame
system.time(
  for(sex_i in c("Male", "Female")){
    print(sex_i)
    #for(state_i in c("Alabama", "Arizona", "Arkansas", "California")) { #saved as results_set_1
    #for(state_i in c("Colorado", "Connecticut", "Delaware", "Washington DC")) { #saved as results_set_2
    for(state_i in c("Florida", "Georgia", "Illinois", "Indiana")) { #saved as results_set_3  
      print(state_i)
      assign(paste0("r.White.", gsub(" ", "", state_i), ".", sex_i), run_analysis(dataset = dat.clean, state1 = state_i, sex1 = sex_i, race1 = "White"))
      assign(paste0("r.Black.", gsub(" ", "", state_i), ".", sex_i), run_analysis(dataset = dat.clean, state1 = state_i, sex1 = sex_i, race1 = "Black"))
    }
  }
)

# r.White <- rbind(r.White.AlabamaMale, r.White.ArizonaMale, r.White.ArkansasMale, r.White.CaliforniaMale,
#                  r.White.AlabamaFemale, r.White.ArizonaFemale, r.White.ArkansasFemale, r.White.CaliforniaFemale)
# r.White <- rbind(r.White.Colorado.Male, r.White.Connecticut.Male, r.White.Delaware.Male, r.White.WashingtonDC.Male,
#                  r.White.Colorado.Female, r.White.Connecticut.Female, r.White.Delaware.Female, r.White.WashingtonDC.Female)
r.White <- rbind(r.White.Florida.Male, r.White.Georgia.Male, r.White.Illinois.Male, r.White.Indiana.Male,
                 r.White.Florida.Female, r.White.Georgia.Female, r.White.Illinois.Female, r.White.Indiana.Female)
r.White$race <- "White"

# r.Black <- rbind(r.Black.AlabamaMale, r.Black.ArizonaMale, r.Black.ArkansasMale, r.Black.CaliforniaMale,
#                  r.Black.AlabamaFemale, r.Black.ArizonaFemale, r.Black.ArkansasFemale, r.Black.CaliforniaFemale)
r.Black <- rbind(r.Black.Florida.Male, r.Black.Georgia.Male, r.Black.Illinois.Male, r.Black.Indiana.Male,
                 r.Black.Florida.Female, r.Black.Georgia.Female, r.Black.Illinois.Female, r.Black.Indiana.Female)
r.Black$race <- "Black"
```

@@

le.calculations = vector(mode = "list", length = n)

counter = 1
system.time(
  for (stratum_i in levels(droplevels(r.All$state.year.sex))){

@@

#SET 2: Colorado, Connecticut, Delaware, Washington DC
# save(r.All, le.calculations, file = "~/BW_results/results_set_2.Rdata") 
# write.csv(x = BlackWhite, file = "~/BlackWhiteMortalityGap/Results/BlackWhite_set_2.csv")
# write.csv(x = age.decomp.estimates, file = "~/BlackWhiteMortalityGap/Results/age_decomp_set_2.csv")
# write.csv(x = cod.marginal.estimates, file = "~/BlackWhiteMortalityGap/Results/cod_marginal_set_2.csv")
# write.csv(x = age.cod.estimates, file = "~/BlackWhiteMortalityGap/Results/age_cod_set_2.csv")

#SET 3: Florida, Georgia, Illinois, Indiana
save(r.All, le.calculations, file = "~/BW_results/results_set_3.Rdata") 
write.csv(x = BlackWhite, file = "~/BlackWhiteMortalityGap/Results/BlackWhite_set_3.csv")
write.csv(x = age.decomp.estimates, file = "~/BlackWhiteMortalityGap/Results/age_decomp_set_3.csv")
write.csv(x = cod.marginal.estimates, file = "~/BlackWhiteMortalityGap/Results/cod_marginal_set_3.csv")
write.csv(x = age.cod.estimates, file = "~/BlackWhiteMortalityGap/Results/age_cod_set_3.csv")
```
